---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chatrbox

chatrbox was motivated by the Posit Open Source group's Spring Cleaning, where we all focus for a week on the parts of package maintenance
that don't often come to the top of the priority list.

chatrbox has one function, `gc_prompt()` that sends a prompt to ChatGPT
in the form: "Write {format} about {topic} in the style of {style}".
By default, `format`, `topic`, and `style` are randomly chosen from a 
list, but you can choose them yourself. The pre-populated list of topics
was motivated by our Spring Cleaning activities.

## Installation

You can install the development version of chatrbox like so:

``` r
# install.packages("pak")
pak::pak("ateucher/chatrbox")
```

## Examples

Using the defaults:

```{r example}
library(chatrbox)

chatrbox()
```

With custom prompts:

```{r}
chatrbox(format = "a short political speech", 
         topic = "why R progammers love cats", 
         style = "Mary Poppins")
```
